---
title: "MA 2611 Lab5"
author: "Jacob Nguyen"
date: "2022-09-29"
output:
  pdf_document: default
  html_document: default
---
1. In an eighth grade English class, the recent scores of an exam followed a normal 
distribution X~N(78,36). Calculate the following:
a. The proportion of the class expected to score below 50
```{r}
pnorm(q=50,mean=78,sd=6)
```

b. The proportion of the class expected to score above 90
```{r}
1 - pnorm(q=90,mean=78,sd=6)
```

c. The proportion of the class expected to score between 60 and 80
```{r}
pnorm(q=80,mean=78,sd=6) - pnorm(q=60,mean=78,sd=6)
```

d. The scores for the first and third quantiles of the class
```{r}
qnorm(p=0.25,mean=78,sd=6)
qnorm(p=0.75,mean=78,sd=6)
```

e. The scores for the  5th and 95th percentiles of the class
```{r}
qnorm(p=0.05,mean=78,sd=6)
qnorm(p=0.95,mean=78,sd=6)
```

 
2. Generate a random sample “x” of 200 observations following X~N(82,51) and create 
a histogram of the sampling distribution of “x.” Calculate the expected value of “x” 
and compare to where the histogram is centralized.  
Is it centralized around E(X) = 82? Why or why not? 
```{r}
x<-rnorm(n=200,mean=82,sd=sqrt(51))
hist(x)
mean(x)
```
It is not centralized around E(X) = 82 because this is a random sample generated and the distribution will not exactly be centered around the given mean, 82.

3. Assume a continuous random variable X~N(0,1). The following sample R code 
generates the histogram and density of the sample mean for n=10: 

a.  Draw the histograms for “xBar”
```{r}
n<-100 # sample size  
sampleN<-1000 # number of samples  
xBar<-array(NA, sampleN) # store values of sample mean for all samples  
 
for (i in 1:sampleN) {  
aSample<-rnorm(n) # generates a sample of size "n" from N(0,1)  
xBar[i]<-mean(aSample) # stores sample mean of all 1000 samples  
}

hist(xBar, freq=FALSE) # histogram for the sample mean  
x<-seq(from=-1, to=1, by=0.005) # defines "x" for plotting  
lines(x, dnorm(x,mean=0,sd=1/sqrt(n)),col="red")

n2<-1000 # sample size  
sampleN<-1000 # number of samples  
xBar2<-array(NA, sampleN) # store values of sample mean for all samples  
 
for (i in 1:sampleN) {  
aSample<-rnorm(n) # generates a sample of size "n" from N(0,1)  
xBar2[i]<-mean(aSample) # stores sample mean of all 1000 samples  
}

hist(xBar2, freq=FALSE) # histogram for the sample mean  
x2<-seq(from=-1, to=1, by=0.005) # defines "x" for plotting  
lines(x, dnorm(x,mean=0,sd=1/sqrt(n)),col="red")
```

b.  Draw the density plots for each “n”
```{r}
plot(x, dnorm(x), type = "l")
plot(x2, dnorm(x2), type = "l")
```

c.  Draw the normal probability plots for “xBar”
```{r}
qqnorm(xBar)
qqline(xBar)
qqnorm(xBar2)
qqline(xBar2)
```

